---
title: "R Markdown"
author: "esra"
date: "2024-04-15"
output:
  html_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
library(ggplot2)
```

## R Markdown

This is an `R` `Markdown` document. Markdown is a simple formatting syntax for authoring HTML, **PDF**, and **MS** Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Include Plots

you can embed plots, for example:

```{r}
plot(pressure)
```

## List

-   bullet list 1

-   bullet list 2

-   bullet list 3

## Format

-   superscript : 2^nd^

-   subscript :CO~2~

-   strike-through: ~~mistake~~

## Code Chunk Options

```{r, eval=FALSE}
gap <- read.csv("gapminder.csv")
```

```{r, warning=FALSE, include=TRUE}
sqrt(-1)
```

## Inline Codes

I want to add some inline codes such as `r sqrt(25)`.

## Tables

| variable 1 | variable 2 | variable 3 |
|------------|------------|------------|
|            |            |            |
|            |            |            |
|            |            |            |

```{r, mytable1}
library(gapminder)
top_gap <- head(gapminder)
knitr::kable(top_gap)
knitr::kable(top_gap, caption = "first row of the dataset,
             gapminder")

```

```{r}
library(tidyverse)
gapminder %>% 
  filter(country == "Turkey") %>% 
  ggplot(aes(x=year, y=lifeExp))+
  geom_point()
```
